Data Processing (Julia)

### 2025-05-03 notebooks/21_model.qmd
feat: fig_juno_sw_comparision

```{julia}
using Discontinuity
using Discontinuity: compute_params!, Alfven_current, inertial_length, gradient_current, uless, plasma_beta
using Juno: produce_or_load_juno
using Juno.Data: read_sw_params_csv
```

```{julia}
using DataFrames, DataFramesMeta
using Unitful

jno_df = produce_or_load_juno()
jno_sw_params = read_sw_params_csv(; add_unit=true)
```

@@

@chain jno_df_with_params begin
    compute_params!
    @transform! begin
        :V_n_cross_sw = @. abs(first(:n_cross) * :V_KMPS)
        :V_n_mva_sw = @. abs(first(:n_mva) * :V_KMPS)
        :d_i_sw = inertial_length.(:N_PROTONS_CC, Unitful.q, Unitful.mp)
        :J_A_sw = Alfven_current.(:B_mag, :N_PROTONS_CC)
        :β_sw = plasma_beta.(:T_PROTONS_EV, :N_PROTONS_CC, :B_mag)
    end
    @transform! @astable begin
        :L_n_cross_sw = :V_n_cross_sw .* :duration
        :L_n_cross_sw_norm = @. :L_n_cross_sw / :d_i_sw |> NoUnits
        :J_m_max_cross_sw = @. abs(gradient_current(:grad, :V_n_cross_sw))
        :J_m_max_cross_sw_norm = @. :J_m_max_cross_sw / :J_A_sw |> NoUnits

@@

```{julia}
using CairoMakie
import CairoMakie.Makie.SpecApi as S
using UnitfulLatexify: latexroundunitlabel as lru

@@

let df = jno_df_with_params, xlabel = "Model", ylabel = "Juno", axis = (; xscale=log10, yscale=log10), plot = (; alpha=0.3)
    f = Figure()
    ax1 = Axis(f[1, 1]; title=lru("V", u"km/s"), ylabel)
    ax2 = Axis(f[1, 2]; title=lru("n", u"cm^-3"), axis...)

    ax_T = Axis(f[2, 1]; title=lru("T", u"eV"), axis...)
    ax_β = Axis(f[2, 2]; title=lru("β", u""), axis...)

    ax3 = Axis(f[4, 1]; title=lru("L", u"km"), ylabel, axis...)
    ax4 = Axis(f[4, 2]; title=lru("J", u"nA/m^2"), axis...)
    ax5 = Axis(f[5, 1]; title=L"L/d_i", xlabel, ylabel, axis...)
    ax6 = Axis(f[5, 2]; title=L"J/J_{Alfven}", xlabel, axis...)

    @with df begin
        uless_plot!(ax1, :V_mag, :V_KMPS)
        uless_plot!(ax2, :n, :N_PROTONS_CC)

        p1 = uless_plot!(ax3, :L_n_cross, :L_n_cross_sw, label="Cross"; plot...)
        p2 = uless_plot!(ax3, :L_n_mva, :L_n_mva_sw, label="MVA"; plot...)
        Legend(f[3, :], [p1, p2], ["Cross", "MVA"])

        uless_plot!(ax_T, :T, :T_PROTONS_EV)
        uless_plot!(ax_β, :β, :β)

        uless_plot!(ax4, :J_m_max_cross, :J_m_max_cross_sw, label="Cross"; plot...)
        uless_plot!(ax4, :J_m_max_mva, :J_m_max_mva_sw, label="MVA"; plot...)
        uless_plot!(ax5, :L_n_cross_norm, :L_n_cross_sw_norm; plot...)
        uless_plot!(ax5, :L_n_mva_norm, :L_n_mva_sw_norm; plot...)
        uless_plot!(ax6, :J_m_max_cross_norm, :J_m_max_cross_sw_norm; plot...)
        uless_plot!(ax6, :J_m_max_mva_norm, :J_m_max_mva_sw_norm; plot...)
    end

@@

    lines!(ax2, exp10.(-1:0), exp10.(-1:0); color, linestyle)
    lines!(ax3, exp10.([2, 4.5]), exp10.([2, 4.5]); color, linestyle)
    lines!(ax4, exp10.(-2:1), exp10.(-2:1); color, linestyle)
    lines!(ax5, exp10.(-1:2), exp10.(-1:2); color, linestyle)
    lines!(ax6, exp10.(-2:1), exp10.(-2:1); color, linestyle)

    limits!(ax1, 360, 550, 360, 550)

    easy_save("model/juno_sw_comparision")
end
```

>>>>

```{julia}
using Discontinuity
using Discontinuity: compute_params!, Alfven_current, inertial_length, gradient_current, uless, plasma_beta, filter_low_mva_quality!
using Juno: produce_or_load_juno
using Juno.Data: get_mag_data, get_state_data, read_sw_params_csv
using CairoMakie
using AlgebraOfGraphics
import SPEDAS
set_aog_theme!()
theme = Theme(; figure_padding=(0, 6, 0, 0),
    Legend=(padding=(0, 0, 0, 0), margin=(0, 0, 0, 0),)
)
update_theme!(theme)
```

```{julia}
using DataFrames, DataFramesMeta, DimensionalData
using Unitful

jno_df = produce_or_load_juno()
n, V, T, r = get_state_data()
jno_sw_params = read_sw_params_csv(; add_unit=true)

selector = Ti(Near(jno_df.time))
jno_df.r = parent(r[selector])
jno_df.T = parent(T[selector]) * u"K"
```

@@

@chain jno_df_with_params begin
    compute_params!
    @transform! begin
        :V_n_cross_sw = @. abs(first(:n_cross) * :V_KMPS)
        :V_n_mva_sw = @. abs(first(:n_mva) * :V_KMPS)
        :d_i_sw = inertial_length.(:N_PROTONS_CC)
        :J_A_sw = Alfven_current.(:B_mag, :N_PROTONS_CC)
        :β_sw = plasma_beta.(:T_PROTONS_EV, :N_PROTONS_CC, :B_mag)
    end
    @transform! @astable begin
        :L_n_cross_sw = :V_n_cross_sw .* :duration
        :L_n_cross_sw_norm = @. :L_n_cross_sw / :d_i_sw |> NoUnits
        :J_m_max_cross_sw = @. abs(gradient_current(:grad, :V_n_cross_sw))
        :J_m_max_cross_sw_norm = @. :J_m_max_cross_sw / :J_A_sw |> NoUnits

@@

```{julia}
using UnitfulLatexify: latexroundunitlabel as lru
using Beforerr

@@

let df = filter_low_mva_quality!(jno_df_with_params), xlabel = "Model", ylabel = "Juno", axis = (; xscale=log10, yscale=log10), plot = (; alpha=0.3)
    f = Figure(;)
    wh = (width=120, height=110)
    ax1 = Axis(f[1, 1]; title=lru("V", u"km/s"), ylabel, wh...)
    ax2 = Axis(f[1, 2]; title=lru("n", u"cm^-3"), wh..., axis...)

    ax_T = Axis(f[1, 3]; title=lru("T", u"eV"), wh..., axis...)
    ax_β = Axis(f[1, 4]; title=L"β", wh..., axis...)

    ax_L = Axis(f[2, 1]; title=lru("L", u"km"), xlabel, ylabel, wh..., axis...)
    ax_J = Axis(f[2, 2]; title=lru("J", u"nA/m^2"), xlabel, wh..., axis...)
    ax_Ln = Axis(f[2, 3]; title=L"L/d_i", xlabel, wh..., axis...)
    ax_Jn = Axis(f[2, 4]; title=L"J/J_A", xlabel, wh..., axis...)

    @with df begin
        uless_plot!(ax1, :V_mag, :V_KMPS)
        uless_plot!(ax2, :n, :N_PROTONS_CC)
        uless_plot!(ax_T, :T, :T_PROTONS_EV)
        uless_plot!(ax_β, :β, :β_sw)

        p1 = uless_plot!(ax_L, :L_n_cross, :L_n_cross_sw, label="Cross"; plot...)
        p2 = uless_plot!(ax_L, :L_n_mva, :L_n_mva_sw, label="MVA"; plot...)
        axislegend(ax_L; padding=0, position=(^(:lt)), framevisible=true, framecolor=(^(:gray)))

        uless_plot!(ax_J, :J_m_max_cross, :J_m_max_cross_sw; plot...)
        uless_plot!(ax_J, :J_m_max_mva, :J_m_max_mva_sw; plot...)
        uless_plot!(ax_Ln, :L_n_cross_norm, :L_n_cross_sw_norm; plot...)
        uless_plot!(ax_Ln, :L_n_mva_norm, :L_n_mva_sw_norm; plot...)
        uless_plot!(ax_Jn, :J_m_max_cross_norm, :J_m_max_cross_sw_norm; plot...)
        uless_plot!(ax_Jn, :J_m_max_mva_norm, :J_m_max_mva_sw_norm; plot...)
    end

@@

    lines!(ax2, exp10.([-1.5, 0]), exp10.([-1.5, 0]); color, linestyle)
    lines!(ax_L, exp10.([2, 5]), exp10.([2, 5]); color, linestyle)
    lines!(ax_J, exp10.(-2:1), exp10.(-2:1); color, linestyle)
    lines!(ax_Ln, exp10.([-1, 3]), exp10.([-1, 3]); color, linestyle)
    lines!(ax_Jn, exp10.([-2, 2]), exp10.([-2, 2]); color, linestyle)
    lines!(ax_T, exp10.([0.2, 1.5]), exp10.([0.2, 1.5]); color, linestyle)
    lines!(ax_β, exp10.(-2:2), exp10.(-2:2); color, linestyle)

    limits!(ax1, 360, 550, 360, 550)
    limits!(ax_L, 10^1.9, 10^5, 10^1.9, 10^5)
    limits!(ax_J, 10^-2.1, 10^1.08, 10^-2.1, 10^1.08)
    limits!(ax_Ln, 10^-1.1, 10^2.8, 10^-1.1, 10^2.8)
    limits!(ax_Jn, 10^-2.5, 10^1.4, 10^-2.5, 10^1.4)

    SPEDAS.add_labels!()
    resize_to_layout!(f)
    easy_save("fig_juno_sw_comparision")
end
```

```{julia}
function query(df, field, f=argmin)
    inds = f(skipmissing(df[!, field]))
    df[inds, :]
end

row = query(jno_df_with_params, :L_n_cross)
```

```{julia}
using SPEDAS: Product, tview, tplot, tlines!
using Discontinuity: MVAProduct
# Juno_B_product = Product(
#     get_mag_data(2016), tview
# )
Juno_B_mva_product = MVAProduct(Juno_B_product, Juno_B_product, row.t_us_ds)

tplot([Juno_B_product, Juno_B_mva_product], row.tstart, row.tstop)
tlines!([row.t_us_ds...])
current_figure()
```

### 2025-05-03 notebooks/30_data.qmd
feat: fig_juno_sw_comparision

```{julia}
using FlexiJoins
using StaticArrays
ds.r = parent(r[Ti(Near(ds.time))])
ds.T = T[Ti(Near(ds.time))] * u"K"

@@

struct FitProduct{F,P} <: Function
    f::F
    param::P
    t0::DateTime
end

function (p::FitProduct)(t0, t1)
    tspan = DateTime(t0):Millisecond(10):DateTime(t1)
    xspan = @. (tspan - p.t0) / Millisecond(1)
    data = p.f.(xspan, Ref(p.param))
    return DimVector(data, Ti(tspan))
end

@@

struct MVAProduct <: Function
    V
    B
    mva_tspan
end

(p::MVAProduct)(t0, t1) = mva(p.V(t0, t1), p.B(p.mva_tspan...))

>>>>

```{julia}
using FlexiJoins
using StaticArrays
selector = Ti(Near(ds.time))
ds.r = parent(r[selector])
ds.T = parent(T[selector]) * u"K"

@@

@@
